Dual host-parasite transcriptomes of apicomplexan \textit{Eimeria falciformis} and its natural mouse host

### 2016-07-13 figures_and_manuscript/manuscript_bmc_format/manuscript_rnaseq.tex
try push 2

\usepackage{graphicx}
\graphicspath{ {../figures/} }
%\def\includegraphic{}
%\def\includegraphics{}

@@

\title{A sample article title}

@@

\author[
   addressref={aff1},                   % id's of addresses, e.g. {aff1,aff2}
   corref={aff1},                       % id of corresponding address, if any
   noteref={n1},                        % id's of article notes, if any
   email={jane.e.doe@cambridge.co.uk}   % email address
]{\inits{JE}\fnm{Jane E} \snm{Doe}}
\author[
   addressref={aff1,aff2},
   email={john.RS.Smith@cambridge.co.uk}
]{\inits{JRS}\fnm{John RS} \snm{Smith}}

@@

\address[id=aff1]{%                           % unique id
  \orgname{Department of Zoology, Cambridge}, % university, etc
  \street{Waterloo Road},                     %
  %\postcode{}                                % post or zip code
  \city{London},                              % city
  \cny{UK}                                    % country
}
\address[id=aff2]{%
  \orgname{Marine Ecology Department, Institute of Marine Sciences Kiel},
  \street{D\"{u}sternbrooker Weg 20},
  \postcode{24105}
  \city{Kiel},
  \cny{Germany}
}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%	METHODS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Methods}
\ldots

\subsection*{Sub-heading for section}
Text for this sub-heading \ldots
\subsubsection*{Sub-sub heading for section}
Text for this sub-sub-heading \ldots
\paragraph*{Sub-sub-sub heading for section}
Text for this sub-sub-sub-heading \ldots
text text text
text text text
text text text
text text text
text text text
text text text
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% Backmatter begins here                   %%
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\usepackage{graphicx}
\graphicspath{ {../} }
%\def\includegraphic{}
%\def\includegraphics{}

@@

\title{Dual host-parasite transcriptomes of apicomplexan \textit{Eimeria falciformis} and its natural mouse host}

@@

\author[
   addressref={aff1},                   % id's of addresses, e.g. {aff1,aff2}
   corref={aff1},                       % id of corresponding address, if any
   noteref={n1},                        % id's of article notes, if any
   email={emanuel.heitlinger@hu-berlin.de}   % email address
]{\inits{EH}\fnm{Emanuel} \snm{Heitlinger}}
\author[
   addressref={aff1},
   %email={john.RS.Smith@cambridge.co.uk}
]{\inits{TK}\fnm{Totta} \snm{Kasemo}}

@@

\address[id=aff1]{%                           % unique id
  \orgname{Department of Biology, Humboldt-Universitat zu Berlin}, % university, etc
  \street{Philippstr. 13, Haus 14},                     %
  %\postcode{}                                % post or zip code
  \city{Berlin},                              % city
  \cny{Germany}                                    % country
}
\address[id=aff2]{%
  \orgname{Marine Ecology Department, Institute of Marine Sciences Kiel},
  \street{D\"{u}sternbrooker Weg 20},
  \postcode{24105}
  \city{Kiel},
  \cny{Germany}
}

@@

\subsubsection*{Data overview}
In total, xx reads were sequenced. For each sample, mouse read numbers were 10⁷ - 10⁸
Quality filters applied resulted in xx reads being removed from further analysis

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%	METHODS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Methods}
\subsection{Mice and infection procedure}
Three strains of mice were used in our experiments: NMRI (Charles River Laboratories, Sulzfeld,
Germany), C57BL/6 (), and Rag1-/- on C57BL/6 background (gift from Susanne Hartmann, FU?). 
Animal procedures were performed according to the German Animal Protection Laws as 
directed and approved by the overseeing authority Landesamt fuer Gesundheit und Soziales 
(Berlin, Germany). Animals where infected as described by Schmid et al., (Schmid12), but
tapwater was used instead of PBS for administration of oocysts. Briefly, NMRI mice were infected 
two times, which will be referred to as first and second infection. For the first infection, 
150 sporulated oocysts were administered in 100 $μ$L by oral gavage. During the first infection
of 60 mice, all animals were weighed every day. On day zero, before infection, as well as on day three,
five and seven days post infection, dpi, caeca from 3-4 sacrificed mice per time point were 
collected. Epithelial cells were isolated as described in Schmid et al.(schmid12). For challenge 
infection, mice recovered for four weeks before second infection. 
Recovery was monitored by weighing and visual inspection of fur. For the second infection, 
1500 sporulated oocysts were applied by oral gavage. Three mice were used as non-second infection control, 
referred to as day 0, second infection.

\subsection{Oocyst purification for infection and sequencing}
Sporulated oocysts were purified by flotation from feces stored in potassium dichromate and 
administered orally in 100 uL tapwater. One \textit{E. falciformis} isolate, 
\textit{E. falciformis} Bayer Haberkorn 1970, was used for all infections and parasite 
samples. The strain is maintained through passage in NMRI mice in our facilities as described 
elsewhere (schmid12).

\subsection{Sporozoite isolation}
Sporozoites were isolated from sporocysts by excystment. For this, sporocysts were incubated at 
37$°$C in DMEM containing 0.04\% tauroglycocholate (MP Biomedicals) and 0.25\% trypsin (Applichem) 
for 30 min. Sporozoites were purified by the method of Schmatz et al (schmatz--).

\subsection{RNA extraction}
Total RNA was isolated from infected epithelial cells, sporozoites and sporulated oocysts 
using Trizol according to the manufacturer’s protocol (Invitrogen). High quality  \emph{what is the meaning of 'high quality' here?}
RNA was used to produce an mRNA library using the Illumina’s TruSeq RNA Sample Preparation guide.
\emph{stolen from genome paper}
Sporozoites were stored in 1 mL Trizol until RNA-isolation. 
Total RNA was isolated using the PureLink RNA Mini Kit (Invitrogen).

\subsection{Sequencing, quality assessment and alignment}
cDNA samples were sequenced by either GAIIX or Illumina Hiseq 2000 as specified in SI xx (both unstranded). Fastq\_quality\_filter was applied to Illumina Hiseq 2000 samples. 
A phred score of 10 was applied. We further set q = 60. These settings require that nine out of ten bases
or more are correct in at least 60\% of the bases for each read.

\subsubsection{Alignment and reference genomes}
We used the published \textit{Mus musculus} mm10 assembly (Genome Reference Consortium Mouse 
Build 38, GCA\_000001635.2) as reference genome including annotations for mouse data. The
\textit{E. falciformis} genome (Heitlinger14) was downloaded from ToxoDB (Gajria07). For the
alignment, the mouse and parasite genome files were merged into a dual reference genome, and 
files including mRNA sequences from both species were aligned against the dual reference genome
using TopHat2 (version 2.0.14, Trapnell09)/ Bowtie2 (version 1.1.2, Langmead12). Single-end and 
pair-end sequence samples were aligned separately with library type 'fr-unstranded' specified 
for pair-end samples. Import into R was enabled by the R package Ballgown, which requires bam 
files to be processed by Tablemaker (Frazee15). Tablemaker in turn makes use of Cufflinks 
(version 2.1.1, Trapnell10).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% Backmatter begins here                   %%
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
